
\begin{thebibliography}{9}
	\bibitem{1}
		P. Aleksic and A. Katsaggelos. Automatic facial expression 				recognition using facial animation parameters and multistream 			hmms. Information Forensics and Security, IEEE Transactions 			on, 1:3–11, March 2006.
		
	\bibitem{15} 
		A. Colmenarez, B. Frey, and T. S. Huang. A probabilistic 				framework for embedded face and facial expression recognition. 		pages 592–597.
 
	\bibitem{22} 
		R. De-Valois and K. De-Valois. Spatial Vision. Oxford Univ. 			Press, New York, 1990.
 
	\bibitem{37} 
		J. Jones and L. Palmer. An evaluation of two-dimensional gabor 		filter model of simple receptive fields in cat striate cortex. 		Journal of Neurophysiology, 58(6):1233–1258,1987.
	\bibitem{41}
		S. Kimura and M. Yachida. Facial expression recognition and 			its degree estimation. In CVPR ’97: Proceedings of the 1997 			Conference on Computer Vision and Pattern Recognition (CVPR 			’97), page 295, Washington, DC, USA, 1997. IEEE Computer 				Society.	
	\bibitem{44}
		I. Kotsia and I. Pitas. Facial expression recognition in image 		sequences using geometric deformation features and support 				vector machines. IEEE Transactions on Image Processing, 16(1):			172–187, 2007.
	\bibitem{61}
		 K. Matsuno, C.-W. Lee, S. Kimura, and S. Tsuji. Automatic 				recognition of human facial expressions. In ICCV ’95: 					Proceedings of the Fifth International Conference on Computer 			Vision, page 352, Washington, DC, USA, 1995. IEEE Computer 				Society.		
	
	\bibitem{76}
		A. Shashua and T. Hazan. Non-negative tensor factorization 				with applications to statistics and computer vision. In ICML 			’05: Proceedings of the 22nd international conference on 				Machine learning, pages 792–799, New York, NY, USA, 2005. ACM.	
	\bibitem{90}
		M. A. O. Vasilescu and D. Terzopoulos. Multilinear analysis of 		image ensembles: Tensorfaces. In ECCV (1), pages 447–460, 				2002.
	\bibitem{92}
		M. A. O. Vasilescu and D. Terzopoulos. Multilinear independent 		components analysis. In CVPR ’05: Proceedings of the 2005 IEEE 		Computer Society Conference on Computer Vision and Pattern 				Recognition (CVPR’05) - Volume 1, pages 547–553, Washington, 			DC, USA, 2005. IEEE Computer Society.
	\bibitem{103}
		 L. Yin and X. Wei. Multi-scale primal feature based facial 			expression modeling and identification. In FGR ’06: 					Proceedings of the 7th International Conference on Automatic 			Face and Gesture Recognition, pages 603–608, Washington, DC, 			USA, 2006. IEEE Computer Society.
	\bibitem{104}
		J. Yu and B. Bhanu. Evolutionary feature synthesis for facial 			expression recognition. Pattern Recogn. Lett., 27(11):1289–				1298, 2006.
\end{thebibliography}